Endogenous Macrodynamics in Algorithmic Recourse

### 2023-01-23 paper/sections/introduction.rmd
final

::: {.example #consumer name="Consumer Credit"}
Suppose Figure \@ref(fig:poc) relates to an automated decision-making system used by a retail bank to evaluate credit applicants with respect to their creditworthiness. Assume that the two features are meaningful in the sense that creditworthiness decreases in the South-East direction. Then we can think of the outcome in panel (d) as representing a situation where the bank supplies credit to more borrowers (blue), but these borrowers are on average less creditworthy and more of them can be expected to default on their loan. This represents a cost to the retail bank.
:::

::: {.example #student name="Student Admission"}
Suppose Figure \@ref(fig:poc) relates to an automated decision-making system used by a university in its student admission process. Assume that the two features are meaningful in the sense that the likelihood of students completing their degree decreases in the South-East direction. Then we can think of the outcome in panel (b) as representing a situation where more students are admitted to university (blue), but they are more likely to fail their degree than students that were admitted in previous years. The university admission committee catches on to this and suspends its efforts to offer Algorithmic Recourse. This represents an opportunity cost to future student applicants, that may have derived utility from being offered recourse.
:::

>>>>

::: {.example #consumer name="Consumer Credit"}
Suppose Figure \@ref(fig:poc) relates to an automated decision-making system used by a retail bank to evaluate credit applicants with respect to their creditworthiness. Assume that the two features are meaningful in the sense that creditworthiness decreases in the bottom-right direction. Then we can think of the outcome in panel (d) as representing a situation where the bank supplies credit to more borrowers (blue), but these borrowers are on average less creditworthy and more of them can be expected to default on their loan. This represents a cost to the retail bank.
:::

::: {.example #student name="Student Admission"}
Suppose Figure \@ref(fig:poc) relates to an automated decision-making system used by a university in its student admission process. Assume that the two features are meaningful in the sense that the likelihood of students completing their degree decreases in the bottom-right direction. Then we can think of the outcome in panel (b) as representing a situation where more students are admitted to university (blue), but they are more likely to fail their degree than students that were admitted in previous years. The university admission committee catches on to this and suspends its efforts to offer Algorithmic Recourse. This represents an opportunity cost to future student applicants, that may have derived utility from being offered recourse.
:::
